Synthesizing Symmetric Lenses

### 2018-07-08 papers/SymmetricLenses/main.tex

% begin evaluation
\section{Evaluation}
\label{sec:evaluation}
We have implemented our symmetric DNF lenses and the synthesis of them as an
extension to Boomerang. We added symmetric lens combinators to Boomerang, and
implemented Boomerang's previous asymmetric lens combinators within the
symmetric lens combinators.

@@

\item How much slower do we perform on bijective lens synthesis benchmarks than
  the existing Optician system customized for bijective lenses.

\item Which heuristics we have described useful for reducing the ``specification
  overhead'' for users? In particular, which heuristics are useful in
  synthesizing the desired lens, instead of merely a lens that satisfies the
  specification.
\end{enumerate}

\subsection{Benchmark Suite}
Our benchmarks are drawn from three different sources.
\begin{enumerate}
\item We adapted \afm{8} data cleaning benchmarks from Flash Fill. In these
  benchmarks, we not only provide functions that clean the data, but we also
  provide other synchronization functions: if the cleaned data is updated, those
  changes are reflected in the original format.
\item We adapted \afm{29} benchmarks from Augeas. These benchmarks turn the
  ad-hoc data present in Linux configuration files into a structured, dictionary
  representation.
\item We used \afm{8} benchmarks from synchronization tasks on synchronizing a
  variety of real-life formats. These formats range from the synchronizing REST
  and JSON web resource descriptions to synchronizing BibTeX and EndNote
  citation descriptions.
\end{enumerate}

A realistic benchmarks suite is cretical in answering the first research
question. To determine whether our algorithm is fast enough to be used in
everyday development, we need to evaluate whether we can solve real-world
problems efficiently. All three of our benchmark sources test real life
problems: the data cleaning tasks presented in Flash Fill are either derived
from online help forums or taken from the Excel product team; Augeas is a
utility that transforms Linux configuration files into a manageable dictionary
form; the many of the remaining benchmarks are from synchronizing real-life data
formats, like BibTeX and EndNote.

>>>>

% begin evaluation
\section{Evaluation}
\label{sec:evaluation}
We have implemented our symmetric DNF lenses and the synthesis of them as an
extension to Boomerang. We added symmetric lens combinators to Boomerang, and
implemented Boomerang's asymmetric lens combinators \sam{all of Boomerang's combinators?} using the symmetric lens combinators.

@@

\item How much slower do we perform on bijective lens synthesis benchmarks than
  the existing Optician system customized for bijective lenses?

\item Which heuristics are useful for reducing the ``specification
  overhead'' for users? In particular, which heuristics are useful in
  synthesizing the desired lens, instead of merely a lens that satisfies the
  specification?
\end{enumerate}

\subsection{Benchmark Suite}
Our benchmarks are drawn from three different sources.
\begin{enumerate}
\item We adapted \afm{8} data cleaning benchmarks from Flash Fill. In these
  benchmarks, we not only provide functions that clean the data, but we also
  provide other synchronization functions: if the cleaned data is updated, those
  changes are reflected in the original format.
\item We adapted \afm{29} benchmarks from Augeas. These benchmarks turn the
  ad-hoc data present in Linux configuration files into a structured, dictionary
  representation. \sam{What does data cleaning mean?}
\item We used \afm{8} benchmarks from synchronization tasks between a
  variety of real-life formats. These tasks range from synchronizing REST
  and JSON web resource descriptions to synchronizing BibTeX and EndNote
  citation descriptions.
\end{enumerate}

A realistic benchmarks suite is critical in answering the first research
question. To determine whether our algorithm is fast enough to be used in
everyday development, we need to evaluate whether we can solve real-world
problems efficiently. All three of our benchmark sources test real life
problems: the data cleaning tasks presented in Flash Fill are either derived
from online help forums or taken from the Excel product team; Augeas is a
utility that transforms Linux configuration files into a manageable dictionary
form; the many of the remaining benchmarks are from synchronizing real-life data
formats, like BibTeX and EndNote.
